Reflections from reproductions

### 2024-08-15 pages/reflections.qmd
feat(reflections): add reflections from anagnostou 2022

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ |

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* <!-- TODO: Check run time of Huang -->
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!----> | <!----> | <!----> |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | ❌ | ❌ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | ❌ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | <!--TODO--> | ❌ |

@@

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ |

@@

@@

For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction. For @kim_modelling_2021, reproduction was facilitated by having relatively simple and repetitive plots which were easy to understand and create.

Fix errors in script. For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.

>>>>

<!--TODO: Add Johnson et al. 2021 reflections once have finished reproduction -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | ✅ | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | <!--TODO--> | <!--TODO--> | ✅ |

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* <!-- TODO: Check run time of Huang -->
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.
* @anagnostou_facs-charm_2022: Model was super quick which made it really easy to run and re-run each time

For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!----> | <!----> | <!----> | <!--TODO--> | N/A |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | <!--TODO--> | N/A |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | ❌ | ❌ | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | ❌ | <!--TODO--> | <!--TODO--> | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | <!--TODO--> | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | ✅ | <!--TODO--> | N/A |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | <!--TODO--> | <!--TODO--> | N/A |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | <!--TODO--> | ❌ | <!--TODO--> | ✅ |

@anagnostou_facs-charm_2022: Outputs to `OUT_STATS.csv`.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |

@@

@anagnostou_facs-charm_2022: The layout of the results spreadsheet was simple, understandable and easy to read, making it easy to adapt into figures.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ |

@@

@anagnostou_facs-charm_2022: The authors included a random seed so the results I got were identical to the original (so no need for any subjectivity in deciding whether its similar enough, as I could perfectly reproduce).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ |

@@

## Documentation

## Include instructions on how to run the model/script

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |

@anagnostou_facs-charm_2022: Clear README with instructions on how to run the model was really helpful.

@@

For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction. For @kim_modelling_2021, reproduction was facilitated by having relatively simple and repetitive plots which were easy to understand and create. For @anagnostou_facs-charm_2022, the figures were simple (just means and CI which are already calculated).

Fix errors in script. For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end. <!--TODO: Have put in run time, or does it need seperate place -->

@anagnostou_facs-charm_2022: Although not needed for the reproduction itself, when I tried to amend the name and location of the csv file output the model for use in tests, this was very tricky to do as it was hard coded into the scripts and I found difficult to amend due to how the model is run and set up. <!-- TODO: Fall under hard coding? Or output file flexibility? -->

@anagnostou_facs-charm_2022: Included data dictionary for input parameters. Although I didn’t need this, this would have been great if I needed to change the input parameters at all.
